Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-29 paper/related-work.tex
Wordsmithing in Lustre compiler paragraph

There is a fully verified compiler that takes Lustre and turns it into a binary executable that is specified and verified in Coq \cite{10.1145/3140587.3062358}. The key is in combining infinite sequences of data-flow models with incremental manipulation of memories akin to an imperative model. CompCert is used on the backend to create the final rendered executable.

>>>>

A fully verified compiler has been developed that takes Lustre and compiles
it into assembly code, specified and verified in Coq \cite{10.1145/3140587.3062358}.
The key is in combining infinite sequences of data-flow models with incremental
manipulation of memories akin to an imperative model. CompCert is used on the
backend to create the final rendered executable. The work is quite similar to
ours in providing a verified compilation chain from Lustre. However,
there are significant differences: notably, they tackle a more
comprehensive subset of Lustre than our work. We have been able to
work effectively with a relatively simple core language, \eg, without
\emph{clocking} features.  This subset aligns with our contract language, and
allows us to generate behaviorally equivalent code so we can show that the
generated code meets its logical specification.  This, in turn,
can be used as a leaf-level claim in a system-wide correctness argument
conducted by compositional reasoning in AGREE.
